\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}  
\usepackage[scale=0.75]{geometry}

% Personal Info
\name{ALEX }{RUKWARO}
\email{munyirukwaro@gmail.com}
\phone[mobile]{+49 123 456789}
\address{Warschauer Straße 12}{10243, Berlin}{Germany}


\begin{document}
	
	\makecvtitle
	
	% ===== Education =====
	\section{EDUCATION}
	\cventry{2024--Present}
	{B.Sc. Computer Science}
	{GISMA University of Applied Sciences}
	{}
	{}
	{Berlin, Germany}
	
	\cventry{2019--2023:}
	{B.Sc. Software Engineering}
	{University of Northampton}
	{}
	{}
	{Northamptonshire, United Kingdom}
	
	% ===== Experience =====
	\section{EXPERIENCE}
	
	\cventry{2024--Present:}
	{Customer Service Representative(Remote)} 
	{InterFarm K Limited (Family-Owned Business)}
	{Nairobi, Kenya}
	{}
	{
		\begin{itemize}
			\item Adapted to flexible responsibilities common in tight-knit teams (design, inventory, delivery).
			\item Contributed to the personalized service culture typical of family-owned businesses.
			\item Respond to online orders, emails, and live chats
			\item Handle complaints, delivery issues, refunds
		\end{itemize}
	}
	
	\cventry{2023--2024:}
	{Data \& Analytics Graduate Program}
	{Barclays Bank}
	{Northampton, United Kingdom}
	{}
	{
		\begin{itemize}
			\item Selected for the Barclays Competitive Data and Analytics Expert Program, 
			focused on real-world analytics in Retail Banking and Payments.
			\item Delivered data-driven insights on customer segmentation and 
			pricing optimization using SQL, Python, and Power BI.
			\item Collaborated with cross-functional teams to model and interpret large datasets.
			\item Gained exposure to machine learning pipelines, hypothesis testing, and regulatory data practices.
		\end{itemize}	
	}
	
	% ===== Projects =====
	\section{PROJECTS}
	
	\cvitem{Portfolio Website}{
		Designed and developed a personal portfolio using React and TailwindCSS. Includes project showcases, contact form, and smooth animations. 
		\newline
		\textit{GitHub: \href{https://github.com/yourusername/portfolio}{github.com/yourusername/portfolio}}
	}
	
	
	% ===== Skills =====
	\section{SKILLS}
	
	\cvitem{Languages:}{ Typescript, Python, HTML, CSS}
	\cvitem{Tools:}{Git, GitHub, Figma, VS Code}
	\cvitem{Soft Skills:}{Teamwork, Attention to Detail, Time Management}
	\cvitem{Others:}{Floral Design \& Arrangement, Plant \& Flower Care, Visual Merchandising}

	% ===== Interests =====
	\section{INTERESTS}
	
	\cvitem{Outdoor:}{Cinematography, hiking}
	
\end{document}
